Models of VOR learning in MHC knockout mice

### 2013-01-23 Notes/VORmodel.tex
added VOR graphs

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
% arXiv Paper ************************************************
%
% Subhaneil Lahiri's template
%
% Before submitting:
%    Comment out hyperref
%    Comment out showkeys
%    Replace \input{mydefs.tex} with its contents
%       or include mydefs.tex in zip/tar file
%    Replace \input{newsymb.tex} with its contents
%       or include newsymb.tex in zip/tar file
%    Put this file, the .bbl file, any picture or
%       other additional files and natbib.sty
%       file in a zip/tar file
%
% **** -----------------------------------------------------------
\documentclass[12pt]{article}
%Preamble:
\usepackage{a4wide}
\input{sl_preamble.tex}
\input{sl_graphics_preamble.tex}
\graphicspath{{"Figures/"}}
%
% >> Only for drafts! <<
\usepackage[notref,notcite]{showkeys}
% ----------------------------------------------------------------
%\numberwithin{equation}{section}
%\renewcommand{\baselinestretch}{1.5}
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
\newcommand{\inv}{^{-1}}
\newcommand{\dg}{^\mathrm{dg}}
\newcommand{\trans}{^\mathrm{T}}
\newcommand{\I}{\mathbf{I}}
%vec of ones
\newcommand{\onev}{\mathbf{e}}
%mat of ones
\newcommand{\onem}{\mathbf{E}}
%Markov matrix
\newcommand{\MM}{\mathbf{Q}}
%equilibrium distribution
\newcommand{\pr}{\mathbf{p}}
\newcommand{\eq}{\pr^\infty}
%first passage times
\newcommand{\fpt}{\mathbf{T}}
%off-diag first passage times
\newcommand{\fptb}{\overline{\fpt}}
%fundamental matrix
\newcommand{\fund}{\mathbf{Z}}
%other symbols
\newcommand{\Pb}{\mathbf{P}}
\newcommand{\D}{\mathbf{D}}
\newcommand{\pib}{\boldsymbol{\pi}}
\newcommand{\Lb}{\boldsymbol{\Lambda}}
\newcommand{\w}{\mathbf{w}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\frg}{\W^\mathrm{F}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\F}{\boldsymbol{\Phi}}
\DeclareMathOperator{\SNR}{SNR}
\newcommand{\CS}{\mathcal{S}}
\newcommand{\CA}{\mathcal{A}}
\newcommand{\CB}{\mathcal{B}}
\newcommand{\comp}{^\mathrm{c}}
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
\newcommand{\norm}{_0}
\newcommand{\inc}{_{\text{inc}}}
\newcommand{\dec}{_{\text{dec}}}
\newcommand{\incdec}{_{\text{inc/dec}}}
\newcommand{\wt}{_{\text{WT}}}
\newcommand{\kn}{_{\text{D$^\mathrm{b}$K$^\mathrm{b}$-/-}}}
\newcommand{\Kn}{D$^\mathrm{b}$K$^\mathrm{b}$-/-}
\newcommand{\tpre}{t_{\text{pre}}}
% ----------------------------------------------------------------
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title info:
\title{Models of VOR learning in MHC knockout mice}
%
% Author List:
%
\author{Subhaneil Lahiri
%
}

@@

The MHC knockout has a lower threshold for depression.
We can model this by changing $\W\dep\wt$ to $\W\dep\kn$, which should have larger matrix elements.

QUESTION: Should $f\pot\wt=f\pot\kn$?

@@

On the other hand, one could imagine adjusting $f\pot\wt$ and $f\pot\kn$ so that $\eq\wt\w = \eq\kn\w$.
But, now that the synaptic weights are the same, the electrical activity will be the same, and there will be no reason to expect different statistics for potentiation or depression.

@@

For the cascade model, we will use the same value for the parameter $x$ (which controls the decay of transition rates, see \cite{Fusi2005cascade}) for potentiation and depression in the wild-type as well as potentiation in the \Kn\ mutant. 
We will use a larger value for $x$ for depression in the \Kn\ mutant.

For the multistate and two state models, we will use the same value for the transition probabilities, $q$ for potentiation and depression in the wild-type as well as potentiation in the \Kn\ mutant. 
We will use a larger value for $q$ for depression in the \Kn\ mutant.

@@

\begin{figure}
 \begin{center}
 \begin{myenuma}
  \item\aligntop{\includegraphics[height=2cm]{cascade.svg}}\label{fig:cascade}\hspace{0.5cm}
  \item\aligntop{\includegraphics[height=1.7cm]{multistate.svg}}\label{fig:multistate}\hspace{0.5cm}
  \item\aligntop{\includegraphics[height=1.7cm]{binary.svg}}\label{fig:binary}
 \end{myenuma}
 \end{center}
  \caption{Transition probabilities for different models. 
  (\ref{fig:cascade}) In the cascade model, the transition probabilities decay geometrically with a parameter $x$ (see \cite{Fusi2005cascade}).
  (\ref{fig:multistate}) In the multistate model the transition probabilities for potentiation/depression are all equal and it is parameterised by these two values.
  (\ref{fig:binary}) The two-state model is parameterised by the two transition probailities.}\label{fig:models}
\end{figure}

\begin{table}
 \begin{center}
  \begin{tabular}{|l|c|c|c|c|}
    \hline
    % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
    Model & \# states & pot,WT dep & \Kn\ dep & $\Delta f$\\
    \hline
    Cascade    & 10 & $x=0.25$ & $x=0.33$ & -0.3 \\
    Multistate & 10 & $q=0.6$  & $q=0.8$  & -0.1 \\
    Two-state  & 2  & $q=0.6$  & $q=0.8$  & -0.1 \\
    \hline
  \end{tabular}
 \end{center}
  \caption{Parameters used in simulations.}\label{tab:params}
\end{table}

@@

@@

@@

Now, consider the mutant, for which $q\pot=\beta q\dep=q$, $\beta<1$.
Without pre-training:
%
\begin{equation}\label{eq:multiKNnopre}
  \Phi = -\frac{2(1-\beta)\beta^{M/2-1}\Delta fq}{1-\beta^M}.
\end{equation}
%
With pre-training:
%
\begin{equation}\label{eq:multiKnpre}
\begin{aligned}
  \Phi &= -4\Delta f q \, \frac{(1-2\Delta f) - \beta(1+2\Delta f)}
          {(1-2\Delta f)^M - \beta^M(1+2\Delta f)^M}   \,
          \beta^{M/2-1}(1-2\Delta f)^{M/2-1} (1+2\Delta f)^{M/2-1}.
\end{aligned}
\end{equation}
%

@@

@@

Now, consider the mutant, for which $q\pot=\beta q\dep=q$, $\beta<1$.
Without pre-training:
%
\begin{equation}\label{eq:binKNnopre}
  \Phi = -\frac{2\Delta f q}{1+\beta},
\end{equation}
%
which is always larger that \eqref{eq:binWTnopre}.
With pre-training:
%
\begin{equation}\label{eq:binKnpre}
\begin{aligned}
  \Phi &= -4\Delta f q \, \frac{(1-2\Delta f) - \beta(1+2\Delta f)}
          {(1-2\Delta f)^2 - \beta^2(1+2\Delta f)^2}.
\end{aligned}
\end{equation}
%

>>>>

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
% arXiv Paper ************************************************
%
% Subhaneil Lahiri's template
%
% Before submitting:
%    Comment out hyperref
%    Comment out showkeys
%    Replace \input{mydefs.tex} with its contents
%       or include mydefs.tex in zip/tar file
%    Replace \input{newsymb.tex} with its contents
%       or include newsymb.tex in zip/tar file
%    Put this file, the .bbl file, any picture or
%       other additional files and natbib.sty
%       file in a zip/tar file
%
% **** -----------------------------------------------------------
\documentclass[12pt]{article}
%Preamble:
\usepackage{a4wide}
\input{sl_preamble.tex}
\input{sl_graphics_preamble.tex}
\graphicspath{{"Figures/"}}
%
% >> Only for drafts! <<
\usepackage[notref,notcite]{showkeys}
% ----------------------------------------------------------------
%\numberwithin{equation}{section}
%\renewcommand{\baselinestretch}{1.5}
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
\newcommand{\inv}{^{-1}}
\newcommand{\dg}{^\mathrm{dg}}
\newcommand{\trans}{^\mathrm{T}}
\newcommand{\I}{\mathbf{I}}
%vec of ones
\newcommand{\onev}{\mathbf{e}}
%mat of ones
\newcommand{\onem}{\mathbf{E}}
%Markov matrix
\newcommand{\MM}{\mathbf{Q}}
%equilibrium distribution
\newcommand{\pr}{\mathbf{p}}
\newcommand{\eq}{\pr^\infty}
%first passage times
\newcommand{\fpt}{\mathbf{T}}
%off-diag first passage times
\newcommand{\fptb}{\overline{\fpt}}
%fundamental matrix
\newcommand{\fund}{\mathbf{Z}}
%other symbols
\newcommand{\Pb}{\mathbf{P}}
\newcommand{\D}{\mathbf{D}}
\newcommand{\pib}{\boldsymbol{\pi}}
\newcommand{\Lb}{\boldsymbol{\Lambda}}
\newcommand{\w}{\mathbf{w}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\frg}{\W^\mathrm{F}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\F}{\boldsymbol{\Phi}}
\DeclareMathOperator{\SNR}{SNR}
\newcommand{\CS}{\mathcal{S}}
\newcommand{\CA}{\mathcal{A}}
\newcommand{\CB}{\mathcal{B}}
\newcommand{\comp}{^\mathrm{c}}
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
\newcommand{\norm}{_0}
\newcommand{\inc}{_{\text{inc}}}
\newcommand{\dec}{_{\text{dec}}}
\newcommand{\incdec}{_{\text{inc/dec}}}
\newcommand{\wt}{_{\text{WT}}}
\newcommand{\ko}{_{\text{D$^\mathrm{b}$K$^\mathrm{b}$-/-}}}
\newcommand{\KO}{D$^\mathrm{b}$K$^\mathrm{b}$-/-}
\newcommand{\tpre}{t_{\text{pre}}}
% ----------------------------------------------------------------
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title info:
\title{Models of VOR learning in MHC knockout mice}
%
% Author List:
%
\author{Subhaneil Lahiri
%
}

@@

The MHC knockout has a lower threshold for depression.
We can model this by changing $\W\dep\wt$ to $\W\dep\ko$, which should have larger matrix elements.

QUESTION: Should $f\pot\wt=f\pot\ko$?

@@

On the other hand, one could imagine adjusting $f\pot\wt$ and $f\pot\ko$ so that $\eq\wt\w = \eq\ko\w$.
But, now that the synaptic weights are the same, the electrical activity will be the same, and there will be no reason to expect different statistics for potentiation or depression.
If we did this for the multistate or two-state models, we'd remove all differences between the wild-type and \KO\ knockout.

@@

For the cascade model, we will use the same value for the parameter $x$ (which controls the decay of transition rates, see \cite{Fusi2005cascade}) for potentiation and depression in the wild-type as well as potentiation in the \KO\ mutant.
We will use a larger value for $x$ for depression in the \KO\ mutant.

For the multistate and two state models, we will use the same value for the transition probabilities, $q$ for potentiation and depression in the wild-type as well as potentiation in the \KO\ mutant.
We will use a larger value for $q$ for depression in the \KO\ mutant.

@@

\begin{figure}
 \begin{center}
 \begin{myenuma}
  \item\aligntop{\includegraphics[height=2cm]{cascade.svg}}\label{fig:cascade}\hspace{0.5cm}
  \item\aligntop{\includegraphics[height=1.7cm]{multistate.svg}}\label{fig:multistate}\hspace{0.5cm}
  \item\aligntop{\includegraphics[height=1.7cm]{binary.svg}}\label{fig:binary}
 \end{myenuma}
 \end{center}
  \caption{Transition probabilities for different models.
  (\ref{fig:cascade}) In the cascade model, the transition probabilities decay geometrically with a parameter $x$ (see \cite{Fusi2005cascade}).
  (\ref{fig:multistate}) In the multistate model the transition probabilities for potentiation/depression are all equal and it is parameterised by these two values.
  (\ref{fig:binary}) The two-state model is parameterised by the two transition probailities.} \label{fig:models}
\end{figure}

\begin{table}
 \begin{center}
  \begin{tabular}{|l|c|c|c|c|c|c|}
    \hline
    % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
    Model & \# states & pot,WT dep & \KO\ dep & $\Delta f$ & $rt_\text{train}$ & $rt_\text{pre}$ \\
    \hline
    Cascade    & 10 & $x=0.25$ & $x=0.33$ & -0.3 & 50 & 50 \\
    Cascade    & 10 & $x=0.25$ & $x=0.33$ & -0.3 & 50 & 150 \\
    Multistate & 10 & $q=0.6$  & $q=0.8$  & -0.1 & 50 & 50 \\
    Multistate & 10 & $q=0.6$  & $q=0.8$  & -0.4 & 20 & 20 \\
    Two-state  & 2  & $q=0.4$  & $q=0.8$  & -0.1 & 5 & 5 \\
    \hline
  \end{tabular}
 \end{center}
  \caption{Parameters used in simulations.} \label{tab:params}
\end{table}

@@

\begin{figure}
 \begin{center}
 \begin{myenuma}
  \item\aligntop{\includegraphics[width=7cm]{cascade_short_learn.eps}}\label{fig:cascade_short_learn}
  \item\aligntop{\includegraphics[width=7cm]{cascade_short_learnS.eps}}\label{fig:cascade_short_learnS}
  \item\label{fig:cascade_short_eq}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=7cm]{cascade_short_eq_WT.eps}}\label{fig:cascade_short_eq_WT}
                    \item\aligntop{\includegraphics[width=7cm]{cascade_short_eq_KO.eps}}\label{fig:cascade_short_eq_KO}
                  \end{myenumi}
  \item\label{fig:cascade_short_pr}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=3cm]{cascade_short_pr_WT_nopre.eps}}\label{fig:cascade_short_pr_WT_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{cascade_short_pr_WT_pre.eps}}\label{fig:cascade_short_pr_WT_pre}
                    \item\aligntop{\includegraphics[width=3cm]{cascade_short_pr_KO_nopre.eps}}\label{fig:cascade_short_pr_KO_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{cascade_short_pr_KO_pre.eps}}\label{fig:cascade_short_pr_KO_pre}
                  \end{myenumi}
 \end{myenuma}
 \end{center}
  \caption{Simulation results for cascade model with short pre-training ($rt_\text{pre}=50$).
  (\ref{fig:cascade_short_learn}) Learning curves for wild-type and \KO\ knockout with and without pre-training.
  (\ref{fig:cascade_short_learnS}) Learning curves restricted to gain-increase training.
  (\ref{fig:cascade_short_eq}) Equilibrium distributions without training or with gain-increase/decrease training for (\ref{fig:cascade_short_eq_WT}) wild-type and (\ref{fig:cascade_short_eq_KO}) \KO\ knockout.
  (\ref{fig:cascade_short_pr}) Evolution of probability distributions for (\ref{fig:cascade_short_pr_WT_nopre}\ref{fig:cascade_short_pr_WT_pre}) wild-type and  (\ref{fig:cascade_short_pr_KO_nopre}\ref{fig:cascade_short_pr_KO_pre}) \KO\ knockout without (\ref{fig:cascade_short_pr_WT_nopre},\ref{fig:cascade_short_pr_KO_nopre}) and with (\ref{fig:cascade_short_pr_WT_pre},\ref{fig:cascade_short_pr_KO_pre}) pre-training. } \label{fig:cascade_short}
\end{figure}

\begin{figure}
 \begin{center}
 \begin{myenuma}
  \item\aligntop{\includegraphics[width=7cm]{cascade_long_learn.eps}}\label{fig:cascade_long_learn}
  \item\aligntop{\includegraphics[width=7cm]{cascade_long_learnS.eps}}\label{fig:cascade_long_learnS}
  \item\label{fig:cascade_long_eq}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=7cm]{cascade_long_eq_WT.eps}}\label{fig:cascade_long_eq_WT}
                    \item\aligntop{\includegraphics[width=7cm]{cascade_long_eq_KO.eps}}\label{fig:cascade_long_eq_KO}
                  \end{myenumi}
  \item\label{fig:cascade_long_pr}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=3cm]{cascade_long_pr_WT_nopre.eps}}\label{fig:cascade_long_pr_WT_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{cascade_long_pr_WT_pre.eps}}\label{fig:cascade_long_pr_WT_pre}
                    \item\aligntop{\includegraphics[width=3cm]{cascade_long_pr_KO_nopre.eps}}\label{fig:cascade_long_pr_KO_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{cascade_long_pr_KO_pre.eps}}\label{fig:cascade_long_pr_KO_pre}
                  \end{myenumi}
 \end{myenuma}
 \end{center}
  \caption{Simulation results for cascade model with long pre-training ($rt_\text{pre}=150$).
  (\ref{fig:cascade_long_learn}) Learning curves for wild-type and \KO\ knockout with and without pre-training.
  (\ref{fig:cascade_long_learnS}) Learning curves restricted to gain-increase training.
  (\ref{fig:cascade_long_eq}) Equilibrium distributions without training or with gain-increase/decrease training for (\ref{fig:cascade_long_eq_WT}) wild-type and (\ref{fig:cascade_long_eq_KO}) \KO\ knockout.
  (\ref{fig:cascade_long_pr}) Evolution of probability distributions for (\ref{fig:cascade_long_pr_WT_nopre}\ref{fig:cascade_long_pr_WT_pre}) wild-type and  (\ref{fig:cascade_long_pr_KO_nopre}\ref{fig:cascade_long_pr_KO_pre}) \KO\ knockout without (\ref{fig:cascade_long_pr_WT_nopre},\ref{fig:cascade_long_pr_KO_nopre}) and with (\ref{fig:cascade_long_pr_WT_pre},\ref{fig:cascade_long_pr_KO_pre}) pre-training. } \label{fig:cascade_long}
\end{figure}

@@

\begin{figure}
 \begin{center}
 \begin{myenuma}
  \item\aligntop{\includegraphics[width=7cm]{multistate_weak_learn.eps}}\label{fig:multistate_weak_learn}
  \item\aligntop{\includegraphics[width=7cm]{multistate_weak_learnS.eps}}\label{fig:multistate_weak_learnS}
  \item\label{fig:multistate_weak_eq}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=7cm]{multistate_weak_eq_WT.eps}}\label{fig:multistate_weak_eq_WT}
                    \item\aligntop{\includegraphics[width=7cm]{multistate_weak_eq_KO.eps}}\label{fig:multistate_weak_eq_KO}
                  \end{myenumi}
  \item\label{fig:multistate_weak_pr}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=3cm]{multistate_weak_pr_WT_nopre.eps}}\label{fig:multistate_weak_pr_WT_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{multistate_weak_pr_WT_pre.eps}}\label{fig:multistate_weak_pr_WT_pre}
                    \item\aligntop{\includegraphics[width=3cm]{multistate_weak_pr_KO_nopre.eps}}\label{fig:multistate_weak_pr_KO_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{multistate_weak_pr_KO_pre.eps}}\label{fig:multistate_weak_pr_KO_pre}
                  \end{myenumi}
 \end{myenuma}
 \end{center}
  \caption{Simulation results for multistate model with weak training ($\Delta f=-0.1$).
  (\ref{fig:multistate_weak_learn}) Learning curves for wild-type and \KO\ knockout with and without pre-training.
  (\ref{fig:multistate_weak_learnS}) Learning curves restricted to gain-increase training.
  (\ref{fig:multistate_weak_eq}) Equilibrium distributions without training or with gain-increase/decrease training for (\ref{fig:multistate_weak_eq_WT}) wild-type and (\ref{fig:multistate_weak_eq_KO}) \KO\ knockout.
  (\ref{fig:multistate_weak_pr}) Evolution of probability distributions for (\ref{fig:multistate_weak_pr_WT_nopre}\ref{fig:multistate_weak_pr_WT_pre}) wild-type and  (\ref{fig:multistate_weak_pr_KO_nopre}\ref{fig:multistate_weak_pr_KO_pre}) \KO\ knockout without (\ref{fig:multistate_weak_pr_WT_nopre},\ref{fig:multistate_weak_pr_KO_nopre}) and with (\ref{fig:multistate_weak_pr_WT_pre},\ref{fig:multistate_weak_pr_KO_pre}) pre-training. } \label{fig:multistate_weak}
\end{figure}

\begin{figure}
 \begin{center}
 \begin{myenuma}
  \item\aligntop{\includegraphics[width=7cm]{multistate_strong_learn.eps}}\label{fig:multistate_strong_learn}
  \item\aligntop{\includegraphics[width=7cm]{multistate_strong_learnS.eps}}\label{fig:multistate_strong_learnS}
  \item\label{fig:multistate_strong_eq}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=7cm]{multistate_strong_eq_WT.eps}}\label{fig:multistate_strong_eq_WT}
                    \item\aligntop{\includegraphics[width=7cm]{multistate_strong_eq_KO.eps}}\label{fig:multistate_strong_eq_KO}
                  \end{myenumi}
  \item\label{fig:multistate_strong_pr}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=3cm]{multistate_strong_pr_WT_nopre.eps}}\label{fig:multistate_strong_pr_WT_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{multistate_strong_pr_WT_pre.eps}}\label{fig:multistate_strong_pr_WT_pre}
                    \item\aligntop{\includegraphics[width=3cm]{multistate_strong_pr_KO_nopre.eps}}\label{fig:multistate_strong_pr_KO_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{multistate_strong_pr_KO_pre.eps}}\label{fig:multistate_strong_pr_KO_pre}
                  \end{myenumi}
 \end{myenuma}
 \end{center}
  \caption{Simulation results for multistate model with strong training ($\Delta f=-0.4$).
  (\ref{fig:multistate_strong_learn}) Learning curves for wild-type and \KO\ knockout with and without pre-training.
  (\ref{fig:multistate_strong_learnS}) Learning curves restricted to gain-increase training.
  (\ref{fig:multistate_strong_eq}) Equilibrium distributions with/without gain-increase/decrease training for (\ref{fig:multistate_strong_eq_WT}) wild-type and (\ref{fig:multistate_strong_eq_KO}) \KO\ knockout.
  (\ref{fig:multistate_strong_pr}) Evolution of probability distributions for (\ref{fig:multistate_strong_pr_WT_nopre}\ref{fig:multistate_strong_pr_WT_pre}) wild-type and  (\ref{fig:multistate_strong_pr_KO_nopre}\ref{fig:multistate_strong_pr_KO_pre}) \KO\ knockout without (\ref{fig:multistate_strong_pr_WT_nopre},\ref{fig:multistate_strong_pr_KO_nopre}) and with (\ref{fig:multistate_strong_pr_WT_pre},\ref{fig:multistate_strong_pr_KO_pre}) pre-training. } \label{fig:multistate_strong}
\end{figure}

@@

Now, consider the mutant, for which $q\pot=\beta q\dep=q$, $\beta<1$.
Without pre-training:
%
\begin{equation}\label{eq:multiKOnopre}
  \Phi = -\frac{2(1-\beta)\beta^{M/2-1}\Delta fq}{1-\beta^M}.
\end{equation}
%
With pre-training:
%
\begin{equation}\label{eq:multiKOpre}
\begin{aligned}
  \Phi &= -4\Delta f q \, \frac{(1-2\Delta f) - \beta(1+2\Delta f)}
          {(1-2\Delta f)^M - \beta^M(1+2\Delta f)^M}   \,
          \beta^{M/2-1}(1-2\Delta f)^{M/2-1} (1+2\Delta f)^{M/2-1}.
\end{aligned}
\end{equation}
%

@@

\begin{figure}
 \begin{center}
 \begin{myenuma}
  \item\aligntop{\includegraphics[width=7cm]{binary_learn.eps}}\label{fig:binary_learn}
  \item\aligntop{\includegraphics[width=7cm]{binary_learnS.eps}}\label{fig:binary_learnS}
  \item\label{fig:binary_eq}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=7cm]{binary_eq_WT.eps}}\label{fig:binary_eq_WT}
                    \item\aligntop{\includegraphics[width=7cm]{binary_eq_KO.eps}}\label{fig:binary_eq_KO}
                  \end{myenumi}
  \item\label{fig:binary_pr}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=3cm]{binary_pr_WT_nopre.eps}}\label{fig:binary_pr_WT_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{binary_pr_WT_pre.eps}}\label{fig:binary_pr_WT_pre}
                    \item\aligntop{\includegraphics[width=3cm]{binary_pr_KO_nopre.eps}}\label{fig:binary_pr_KO_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{binary_pr_KO_pre.eps}}\label{fig:binary_pr_KO_pre}
                  \end{myenumi}
 \end{myenuma}
 \end{center}
  \caption{Simulation results for two-state model.
  (\ref{fig:binary_learn}) Learning curves for wild-type and \KO\ knockout with and without pre-training.
  (\ref{fig:binary_learnS}) Learning curves restricted to gain-increase training.
  (\ref{fig:binary_eq}) Equilibrium distributions without training or with gain-increase/decrease training for (\ref{fig:binary_eq_WT}) wild-type and (\ref{fig:binary_eq_KO}) \KO\ knockout.
  (\ref{fig:binary_pr}) Evolution of probability distributions for (\ref{fig:binary_pr_WT_nopre}\ref{fig:binary_pr_WT_pre}) wild-type and  (\ref{fig:binary_pr_KO_nopre}\ref{fig:binary_pr_KO_pre}) \KO\ knockout without (\ref{fig:binary_pr_WT_nopre},\ref{fig:binary_pr_KO_nopre}) and with (\ref{fig:binary_pr_WT_pre},\ref{fig:binary_pr_KO_pre}) pre-training. } \label{fig:binary_res}
\end{figure}

@@

Now, consider the mutant, for which $q\pot=\beta q\dep=q$, $\beta<1$.
Without pre-training:
%
\begin{equation}\label{eq:binKOnopre}
  \Phi = -\frac{2\Delta f q}{1+\beta},
\end{equation}
%
which is always larger that \eqref{eq:binWTnopre}.
With pre-training:
%
\begin{equation}\label{eq:binKOpre}
\begin{aligned}
  \Phi &= -4\Delta f q \, \frac{(1-2\Delta f) - \beta(1+2\Delta f)}
          {(1-2\Delta f)^2 - \beta^2(1+2\Delta f)^2}.
\end{aligned}
\end{equation}
%
